---
output:
  html_document:
    bibliography: bibtex
    highlight: tango
    keep_md: yes
    theme: spacelab
---

### Data Set

```{r, echo=FALSE}
a <- read.csv(file = "./amnesty.csv", sep=",", header = TRUE)
r <- read.csv(file = "./redcross.csv", sep=",", header = TRUE)
p <- read.csv(file = "./peta.csv", sep=",", header = TRUE)
```


The data sets have been directly retrived with an own Twitter application.

Related Twitter Accounts:

* [Amnesty International][1]

        Number of analyzed tweets: `r length(a[,1])`

* [American Red Cross][2] 

        Number of analyzed tweets: `r length(r[,1])`

* [PETA][3] 
        
        Number of analyzed tweets: `r length(p[,1])`

***

### Notices

This application is primarily a demo to show what is possible. 

In case of any questions related to this application, feel free to write [me a mail.][4]

***

### Used R Packages

```{r, eval=FALSE}
library(graph)
library(twitteR)
library(NLP)
library(tm)
library(shinyIncubator)
library(grid)
library(pvclust)
library(Rgraphviz)
library(qdapTools)
library(qdapRegex)
library(magrittr)
library(wordcloud)
library(RColorBrewer)
library(ggplot2)
library(RCurl)
library(bitops)
library(qdap)
library(devtools)
library(rjson)
library(bit64)
library(httr)
library(SnowballC)
library(slam)
library(RWeka)
library(rJava) 
library(RWekajars)
library(BH)
library(shinyapps)
```

***

### Last Session Info

```{r}
sessionInfo()
```



[1]: https://twitter.com/amnesty "Amnesty Twitter Account"

[2]: https://twitter.com/RedCross "Red Cross Twitter Account"

[3]: https://twitter.com/peta "PETA Twitter Account"

[4]: http://nierhoff.info/#contact "Contact"

***
